PK object batch mode trial

### 2023-07-06 data-raw/batchMode_trial_gpm.Rmd
Updating documentation for methods and added prediction filtering parameters for the plot.pk method
Preliminary finish for the get_tkstats method. Does need more comments and messages.

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5032600",
                                                                   "DTXSID7022253"))
```

@@

Batch mode works, now I need to write a function that recapitulates `coef()` method

@@

@@

# Seems to have worked!
```

@@

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = TRUE)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)

@@

@@

```{r remaining_methods}
# coef_sd
# logLik.pk
# get_tkstats()

my_tkstats <- get_tkstats(my_pk)

plot_results <- plot(my_pk)

>>>>

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5032600"))
```

@@

Batch mode works! Now, I have updated the `coef`, `predict`, `rmse`, and `residuals`
methods.

@@

predict(my_pk,
        exclude = TRUE, # add the "exclude" column to output
        use_scale_conc = TRUE)

@@

@@

plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE, log10_C = FALSE)

my_plot <- plot(my_pk, use_scale_conc = TRUE)

@@

png(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/examplePlot.png",
    width = 8,
    height = 6,
    units = "in",
    res = 150,
    type = "cairo",
    antialias = "none")
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)[[3]]
dev.off()

@@

```{r remaining_methods}
# coef_sd
# logLik.pk
# get_tkstats()
devtools::load_all()
get_tkstats(my_pk) %>% head()
get_tkstats(my_pk) %>% View("TK_test")
my_tkstats <- get_tkstats(my_pk)

# For the July 5th version where it returns a nested dataframe
# 
my_tkstats %>%
  reframe(tkstats_df = purrr::map(c_data,
                                  \(x) {
                                    x %>%
                                      dplyr::rowwise() %>%
                                      dplyr::mutate(
                                        TKstats = sapply(
                                          coefs_vector,
                                          FUN = tk_fun,
                                          route = Route,
                                          medium = Media,
                                          dose = Dose,
                                          time_unit = Time.Units,
                                          conc_unit = Conc.Units,
                                          vol_unit = "L",
                                          simplify = FALSE,
                                          USE.NAMES = TRUE
                                        )
                                      ) %>%
                                      dplyr::ungroup()
                                  })) -> my_tkstats

my_tkstats %>% unnest(cols = c(tkstats_df)) -> my_tkstats

my_tkstats %>% mutate(TKstats_wide  = map(TKstats,
                                     \(x) {
                                       dplyr::select(x, -param_units) %>%
                                         tidyr::pivot_wider(names_from = param_name,
                                                     values_from = param_value)
                                     })) %>%
  unnest(cols = c(TKstats_wide)) %>% View()
